\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-16 article.tex
Better link between sentences

% BG : brain, complex organ
The human brain is a complex biological organ, formed by 100
billions of neurons with 7000 synaptic connections on average.
Cutting edge optical devices have been developed to track in real-time
the neuronal activity of thousands of neurons through a fluorescent
calcium indicator  [todo cite]. Automatic and analytical methods are required to infer
the connectomes from those time series.

The fluorescent calcium image delivers at each acquisition a 2-D view of the
neuron network activities. However, some neurons might not observed or are
confounded with others. The low device sampling rate with respect to neuronal
activity speed might not allow to distinguish neuron activation order,
especially in highly synchronous activity [Stetter and in Stetter [20,46,47]]
of a large part of the network. Moreover the fluorescent concentration is
highly reactive to a neuron activation or a spike, but have a slow decay.

% Introduce notation + goal in mathematical score
% TODO check convention for y_{ij}
The connectomes, the neural network, is represented by a (un)directed graph $G = (V, E)$ comprising
a set of nodes $V$ and a set of edges $E \subseteq \left\{(i, j) \in V \times
V\right\}$, (un)ordered pair from $V$.
Each node $i \in V$ represents a neuron, and each edge $(i, j) \in E$
represents a direct link and interactions between neuron $i$ and a neuron $j$.
In the directed graph, each edges also expresses a causal relationship: an
edge $(i, j) \in E$ indicates that the state of neuron $j$ might be caused
by the neuron $i$. The network inference task is set as follows :
\textit{Given the observations $(x^t \in \mathcal{R}^{|V|})_{t=1}^T $
along $T$ periods of time of the $|V|$ neurons, the goal is to infer the
adjacency matrix $A : a_{i,j} = \mathbb{1}((i, j) \in E)$ of the neural network
of graph $G$, where $\mathbb{1}$ is the indicator function.}

@@

% \textcolor{red}{This section should be rewritten once we get the figure
                % which displayed the effect of the different filters.}

% Defects of the imaging device
% and will have to cope with
% a slower sampling rate than the neuron firing speed, a superposition
% of the activity of several neurons and the slow decay of fluorescent calcium
% indicator.

>>>>

% BG : brain, complex organ
The human brain is a complex biological organ, formed by 100
billions of neurons with 7000 synaptic connections on average.
Cutting edge optical devices delivers in real-time  2-D  images of
the neuronal activity of thousands of neurons through a fluorescent
calcium indicator [todo cite]. Automatic and analytical methods are required to infer
the connectomes from those time series. Furthermore, several experimental issues
have to be handled. Some neurons of the network might not be
observed or are confounded with others. The lower device sampling rate with
respect to neuronal activity speed might not allow to distinguish neuron
activation order, especially in highly synchronous activity
[Stetter and in Stetter [20,46,47]] of a large part of the network. Moreover
the fluorescent concentration is highly reactive to a neuron activation or a
spike, but have a slow decay.

% Introduce notation + goal in mathematical score
The connectomes, the neural network, is represented by a (un)directed graph $G = (V, E)$ comprising
a set of nodes $V$ and a set of edges $E \subseteq \left\{(i, j) \in V \times
V\right\}$, (un)ordered pair from $V$.
Each node $i \in V$ represents a neuron, and each edge $(i, j) \in E$
represents a direct link and interactions between neuron $i$ and a neuron $j$.
In the directed graph, each edges also expresses a causal relationship: an
edge $(i, j) \in E$ indicates that the state of neuron $j$ might be caused
by the neuron $i$. The network inference task is set as follows :
\textit{Given the observations $(x^t \in \mathcal{R}^{|V|})_{t=1}^T $
along $T$ periods of time of the $|V|$ neurons, the goal is to infer the
adjacency matrix $A : a_{i,j} = \mathbb{1}((i, j) \in E)$ of the neural network
of graph $G$, where $\mathbb{1}$ is the indicator function.}

@@
